---
title: "p8105_hw1_qs2261"
author: "Qinting Shen"
date: "2023-09-21"
output: github_document
---

## Problem 1

```{r, echo = FALSE} 
library (moderndive) 
library(tidyverse)
```

Now I will load the `early_january_weather` dataset.

```{r}
data("early_january_weather")
```

* The `early_january_weather` dataset has the information about weather of the first half month of January in 2013 in EWR, which collected data including temperature, dewpoint, humid, wind_dirction, wind_speed, wind_gust, pressure, visibility, etc.

* There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns in the dataset.

* The mean temperature is `r mean (pull(early_january_weather, temp))`.


Now I will make a scatterplot of  `temp` and `time_hour`

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```

This scatterplot indicates that the temperature fluctuated up and down every day, and the temperature shows an overall rising trend, reaching the highest temperature on the 14th. The humidity from Jan 11th to 14th remained a high level (>80).

```{r}
ggsave("scatterplot.pdf")
```



