---
title: "p8105_hw1_qs2261"
author: "Qinting Shen"
date: "2023-09-21"
output: github_document
---

## Problem 1

```{r, echo = FALSE} 
library (moderndive) 
library(tidyverse)
```

Now I will load the `early_january_weather` dataset

```{r}
data("early_january_weather")
```

* The `early_january_weather` dataset has the information about weather of the first half month of January in 2013 in EWR, which collected data including temperature, dewpoint, humid, wind_dirction, wind_speed, wind_gust, pressure, visibility, etc.

* There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns in the dataset.

* The mean temperature is `r round(mean(pull(early_january_weather, temp)), digits=2)` F.


Now I will make a scatterplot of  `temp` and `time_hour`

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```

* This scatterplot indicates that the temperature fluctuated up and down every day, and the temperature shows an overall rising trend, reaching the highest temperature on the 14th. The humidity from Jan 11th to 14th remained a high level (>80).

Save the scatterplot:

```{r}
ggsave("scatterplot.pdf")
```

## Problem 2

Create a dataframe, including

1. `samp`: a random sample of size 10 from a standard Normal distribution
1. `log_vec`: a logical vector indicating whether elements of the sample are greater than 0
1. `char_vec`: a character vector of length 10
1. `fac_vec`: a factor vector of length 10, with 3 different factor “levels”

```{r}
hw1_df= tibble(
  samp = rnorm(10),
  log_vec = samp>0,
  char_vec = c ("A","B","C","D","E","F","G","H","I","J"),
  fac_vec = factor(c("small","medium","large","small","medium","large","small","medium","small","large"))
)
```

Now take the mean of each variable:

```{r}
mean(pull(hw1_df, samp))
mean(pull(hw1_df, log_vec))
mean(pull(hw1_df, char_vec))
mean(pull(hw1_df, fac_vec))
```

* when calculating the mean, random `samp` and `log_vec` works, while `char_vec` and `fac_vec` don't work since they are not numeric or logical.

Write a code chunk that applies the `as.numeric` function to the logical, character, and factor variables

```{r, results='hide'}
as.numeric(pull(hw1_df,log_vec))
as.numeric(pull(hw1_df,char_vec))
as.numeric(pull(hw1_df,fac_vec))
```

* logival_vector: true value was converted to 1, and false value was converted to 0. So, we can calculate the mean of logical vector.
* character_vector: this variable is character type, so it failed to converted to numeric, that's why I got a waring message saying "NAs introduced by coercion". Thus, we cannot calculate the mean of character vector.
* factor_vector: it was converted to number from 1 to 3 following some rules of rank. Although it can be converted to numeric format, they are not true numeric values, so we cannot calculate the mean.

